QPLIB: A Library of Quadratic Programming Instances

### 2017-01-23 QPLIB-2.3.tex
reorganize cutting plane methods
- first the method, then the solvers
- make it clearer that the milp is a relaxation (for CGC)

\paragraph{Cutting plane approaches}.
%
The two remaining solvers in Table \ref{t:solvers} are {\sc AlphaECP} \cite{westerlund} and {\sc DICOpt} \cite{quesada}, which are complete cutting plane methods based on different principles. Characteristic of both solvers is that they need to employ a complete method for solving MILP (LIL) sub-problems at each iteration; in turn, this is typically based on BB, which is therefore a crucial technique also for this class of approaches. Additionally, incomplete methods can be used to provide local solutions. Other solvers, like {\sc BonMin}, also offer this kind of approach among their algorithmic options.

>>>>

\paragraph{Cutting plane approaches.}
%
Cutting plane approaches construct and iteratively improve a MILP (LIL) relaxation of the problem \cite{quesada,westerlund}. The cutting planes for the MILP are generated by linearization (first-order Taylor approximation) of the nonlinearities. If the latter are convex, the MILP provides a valid lower bound for the problem. Additionally, incomplete methods can be used to provide local solutions. Therefor, these methods are complete on CGC if a complete method is used to solve the MILP. The latter is typically based on BB, which is therefore a crucial technique also for this class of approaches.

Solvers in Table \ref{t:solvers} that implement complete cutting plane methods for CGC are {\sc AlphaECP} \cite{westerlund}, {\sc BonMin} (in the algorithmic mode B-OA) \cite{BBCCGLLLMSW} and {\sc DICOpt} \cite{quesada}. \todo{here we give references to the solvers, above we don't}
